Reproducible, flexible and high throughput data extraction from primary literature: The \pkg{metaDigitise} \proglang{R} package

### 2017-11-21 docs/manuscript.tex
Added some small MS changes thanking Dax

\section*{Acknowledgments}
We thanks the I-DEEL group at UNSW for increadibly useful feedback, and a host of colleagues for testing, providing feedback and digitising including: Rose O'Dea, Fonti Kar, Malgorzata Lagisz, Julia Riley, Diego Barneche, Erin Macartney, Gihan Samarasinghe. DWAN was supported by an ARC Discovery Early Career Research Award (DE150101774) and UNSW Vice Chancellors Fellowship and SN an Australian Research Council Future Fellowship (FT130100268).

>>>>

\section*{Acknowledgments}
We thanks the I-DEEL group at UNSW for increadibly useful feedback, and a host of colleagues for testing, providing feedback and digitising including: Rose O'Dea, Fonti Kar, Malgorzata Lagisz, Julia Riley, Diego Barneche, Erin Macartney, Ivan Beltran, Gihan Samarasinghe, Dax Kellie. DWAN was supported by an Australian Research Council Discovery Early Career Research Award (DE150101774) and UNSW Vice Chancellors Fellowship and SN an Australian Research Council Future Fellowship (FT130100268).
